 # QUESTION 1
 Register an application with the Github API here https://github.com/settings/applications.
 Access the API to get information on your instructors repositories (hint
 data to find the time that the datasharing repo was created. What time was it created?
 You may also need to run the code in the base R package and not R studio.
 This tutorial may be useful (https://github.com/hadley/httr/blob/master/demo/oauth2-github.r).
```{r}
library(httr)
library(jsonlite)
library(httpuv)

oauth_endpoints("github")
# Change based on your appname, key, and secret
myapp <- oauth_app("github",
                   key = mykey,
                   secret = myscret
)
# Get OAuth credentials
github_token <- oauth2.0_token(oauth_endpoints("github"), myapp)

# Use API
gtoken <- config(token = github_token)
req <- GET("https://api.github.com/users/jtleek/repos", gtoken)
# Take action on http error
stop_for_status(req)
# Extract content from a request
json1 <- content(req)
# Convert to a data.frame
gitDF = jsonlite::fromJSON(jsonlite::toJSON(json1))

# Subset data.frame
gitDF[gitDF$full_name == "jtleek/datasharing", "created_at"] 
```
#QUESTION 2
The sqldf package allows for execution of SQL commands on R data frames. We will use the sqldf package to practice the queries we might send with the dbSendQuery command in RMySQL.

Download the American Community Survey data and load it into an R object called

acs

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv

Which of the following commands will select only the data for the probability weights pwgtp1 with ages less than 50?

```{r}
library("sqldf")

url <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv"
f <- file.path(getwd(), "ss06pid.csv")
download.file(url, f)
acs <- data.table::data.table(read.csv(f))

# Answer: 
query1 <- sqldf("select pwgtp1 from acs where AGEP < 50")
query1
```
#QUESTION 3
Read this data set into R and report the sum of the numbers in the fourth of the nine columns.

https://d396qusza40orc.cloudfront.net/getdata%2Fwksst8110.for

Original source of the data: http://www.cpc.ncep.noaa.gov/data/indices/wksst8110.for

(Hint this is a fixed width file format)
```{r}
url <- "https://d396qusza40orc.cloudfront.net/getdata%2Fwksst8110.for"
lines <- readLines(url, n = 10)
w <- c(1, 9, 5, 4, 1, 3, 5, 4, 1, 3, 5, 4, 1, 3, 5, 4, 1, 3)
colNames <- c("filler", "week", "filler", "sstNino12", "filler", "sstaNino12", 
              "filler", "sstNino3", "filler", "sstaNino3", "filler", "sstNino34", "filler", 
              "sstaNino34", "filler", "sstNino4", "filler", "sstaNino4")
d <- read.fwf(url, w, header = FALSE, skip = 4, col.names = colNames)
d <- d[, grep("^[^filler]", names(d))]
sum(d[, 4])

# Answer: 
# 32426.7
```

